---
title: "PiUsingCircle"
author: "Paul M"
date: "12/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pseudocode for estimating pi using the circle method
```{r}
set.seed(2053)   # remember to set the random number seed so that you can reproduce your output if you end up needing to hunt bugs

# Let's assume the square has length 2, and is centered at (0,0)
# Set circle radius
CircleRadius<-1

NumberOfTrials<-50000    # how many random points to generate
NumberOfPointsInsideCircle<-0   # this will count how often the point lands inside the circle
```


Do the experiment - here's one way to do it. Let's time the different ways to see how long they take.
```{r method1}
# Start the clock
ptm <- proc.time()

for (i in 1:NumberOfTrials){
  # generate a random point in the square
  # XCoordinate <-   (generate a uniform rv between -CircleRadius and +CircleRadius )
  # YCoordinate <-   (generate a uniform rv between -CircleRadius and +CircleRadius )
  
  # check whether it falls within the circle (i.e. the distance to the origin is less than Circle Radius). If so,
  #if (# add check here)
  {
    NumberOfPointsInsideCircle<-NumberOfPointsInsideCircle+1
  }
  
}

# Calcluate the proportion of points that landed insude the circle
ProportionOfPointsInCircle <- # add code here

# And then do the math to produce you estimate of pi - yours to write
PiEst <- # add calcluation here
cat("\nOur estimate of Pi is (method 1): ",PiEst)

# How long did it take?
TimeTaken <- proc.time()[3] - ptm[3]
cat("\nTotal time: ",TimeTaken)
```


Another way to dso thisa is to generate the x- and y-coordinates for all the points at once, rather than one at a time. If you try doing it that way you should find it runsd a bit more quickly.
Add code for that here...
```{r method2}
# Start the clock
ptm <- proc.time()

#  Add lines of code here
  
# Stop the clock
# How long did it take?
TimeTaken <- proc.time()[3] - ptm[3]
cat("\nTotal time: ",TimeTaken)
```

If you are feeling fancy, write some code to plot your points and the circle and square, 
or plot your current estimate of pi as you perform the iterations

Now you could write some code to repeat the above for different sizes of circle (i.e. different values of CircleRadius). This would be easiest if you turned the above into a function. Does it matter what size you use in terms of efficiency of the algorithm?


