---
title: "UrnVersion2Pseudocode"
author: "Paul M"
date: "12/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pseudcode for the version of the Urn in which there is a "black" ball

The idea here is to build it on your existing code (i.e., define variables in mostly the same way, etc.)
But then you will need to change the function for drawing a ball...
Since you don't know how many colors you will eventually need, it is simpler to notate colors with numbers, so black==0, other colors== 1,2,3...
that way every time you add a new 'color' to the Urn, you can label it with a number
that is one higher than the last number you used.

Your new code for drawing from the Urn will look something like this
```{r outline}

# NumberOfColorsUsed<-NumberOfColorsInUrnAtStart
# while NumberOfBalls<(HowManyBallsWeNeed+1){
  # draw a ball
  # if (Ball is black){
    # pick another ball
    # change color of ball to new color (i.e. new number)
    NumberOfColorsUsed<-NumberOfColorsUsed+1
    # Set color of ball equal to  NumberOfColorsUsed
    # note that we don???t increase the count of the number of balls
    }else{
    # the ball is some other color
    # return the ball and add another one like it
    # increase the counter of how many balls we have in the urn:
    # NumberOfBalls<-NumberOfBalls+1
  #}
```

As before, output summaries of what is in the urn when you are done.
